MS_Intro_Short

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
nearly done on model
ready for comparison

(ii) a prototype software framework we have developed to support the development of transferable CHEMs; and
<!-- propose a set of ethical responsibilities for CHEM project teams and criteria for assessing ethical CHEM implementations; -->
<!-- (ii)  -->
(ii)	how we have applied that software framework to develop and share an initial set of modules for our youth mental health CHEM.

>>>>

(ii) a prototype software framework we have developed to support the development of transferable CHEMs; and
<!-- propose a set of ethical responsibilities for CHEM project teams and criteria for assessing ethical CHEM implementations; -->
<!-- (ii)  -->

(iii)	how we have applied the prototype software framework to undertake initial development of our youth mental health CHEM.

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
ready for comparison

---
title: "MS_Conclusion"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
`r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)` 
<!-- We have identified criteria that can be used to systematically assess the extent to which the computational implementation of health economic models adheres to transparency, reusability and updatability criteria.  -->
Our software framework provides the outline of a technical solution to some of the challenges of transferable CHEM development using open-source and modular approaches. Our framework can be used as a prototype for developing future software frameworks to support implementation of transferable CHEMs. 
<!-- Barriers to ethical CHEM practice arising from resource constraints should be addressed by research funders. -->

>>>>

---
title: "MS_Conclusion"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
`r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)` 
<!-- We have identified criteria that can be used to systematically assess the extent to which the computational implementation of health economic models adheres to transparency, reusability and updatability criteria.  -->
Our software framework provides a solution to some technical barriers we faced when seeking to implement a transferable CHEM in youth mental health. Our framework can be used as a prototype for developing future software frameworks that address the user-requirements of the broader health economic modelling community. 
<!-- Barriers to ethical CHEM practice arising from resource constraints should be addressed by research funders. -->

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
ready for comparison

As illustrated by Table \@ref(tab:checktb), we have developed a prototype software framework that can be used to implement youth mental health CHEMs that largely satisfy our TRU criteria. However, in its current form our software framework is too fragile to be recommended as anything more than a prototype for supporting the development needs of other modelling teams and projects. We developed our prototype software framework primarily to address the user requirements of one group – ourselves. Factors such as user enjoyment, usability, active user-community and supporting resources influence adoption of software frameworks [@myllarniemi2018development]. We currently lack the resources required to  address these issues for our software framework.

However, our prototype has a number of features that future work on CHEM software frameworks may find useful to incorporate. Firstly, developing a software framework to work within an existing and widely used open source programming language such as R, can keep framework scope relatively narrow. This makes it more tractable to develop, maintain and learn, and facilitates integration with other modelling tools written in that language (e.g., the dependency libraries we list in Table \@ref(tab:cpkgs)). Secondly, implementation that combines both object-oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts. Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and Agile Software Development (for which a foundational principle is prioritising the development of working code over writing documentation [@beck2001manifesto]). Our software framework makes this trade off by enforcing the use of consistent code style conventions and file organisation which in turn enables automated generation of simple documentation at every CHEM module update. All model data-structures and algorithms are therefore always documented (at least minimally, with machine authored content), meaning model developers have a requirement to write customised documentation less frequently. Many of the features of our prototype software framework have the potential to be significantly enhanced through integration with evolving code and documentation authoring capabilities of large language models.

Our software framework provides the outline of a technical solution to some of the challenges of open source CHEM development. However, better tools alone are insufficient and policy and institutional changes are also required. <!-- Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful. Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work and funding is rarely adequate to maintain and routinely update a model. Currently, it can take “an extraordinary amount of idealism” to commit to authoring and maintaining research software [@anzt2020environment]. Previously recommended strategies for more beneficial health economic research investments include support for harmonised ethical standards for model development [@10.3389/fpubh.2017.00068], methodological innovation to improve model transferability [@craig2018taking], networks of modellers working on common health conditions [@Sampson2019], and  centralized infrastructure such as open source model repositories [@Pouwels2022] and a standard platform for model implementations [@Ghabri2019]. Development of software frameworks to support ethical CHEM implementations could enable and enhance each of these strategies. --> A future software framework for ethical CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health and health economics, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions. Such approaches will likely be important to ensure a sufficient potential user-base to make CHEM software frameworks sustainable.

>>>>

As illustrated by Table \@ref(tab:checktb), we have developed a software framework and used it to author CHEM modules that largely satisfy explicit criteria for transparency, reusability and updatability. We have used toy data to demonstrate how these CHEM module libraries, originally developed for a single utility mapping study [@Hamilton2021.07.07.21260129], can be applied: (i) to datasets from new samples with different concepts and variable names; (ii) to construct models with different utility instruments, predictors and covariates; and (iii) to develop and use both cross-sectional and longitudinal mapping models.

<!--  it should be noted that  -->Our framework and CHEM module R libraries are currently publicly available as development releases<!-- . When assessing libraries against TRU criteria, we identified the need to write  -->. We plan to undertake a number of key improvements, such as more detailed documentation, comprehensive unit testing and streamlining dependencies,<!-- as part of future quality assurance work required--> prior to submitting these libraries for quality assurance and dissemination by CRAN [@CRAN2022].

Although designed to address challenges specific to our project, ready4 can be a <!-- too fragile to be recommended as anything more than a  -->prototype for future software frameworks that meet the user requirements of other modelling teams and projects. <!-- We developed our prototype software framework primarily to address the user requirements of one group – ourselves.  -->Our prototype has a number of features that such future work can build on.<!-- that future work on CHEM software frameworks may find useful to incorporate. --> Firstly, developing a software framework to work within an existing and widely used open source programming language such as R, can keep framework scope relatively narrow. This makes it more tractable to develop, maintain and learn, and facilitates integration with other modelling tools written in that language (e.g., the dependency libraries we list in Tables \@ref(tab:cpkgs) and \@ref(tab:rfwnlibs)). Secondly, <!-- implementation that combines both object-oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts. Thirdly, -->a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and prioritising the development of working code over writing documentation  (a foundation principle of Agile Software Development [@beck2001manifesto]). Our software framework makes this trade off by enforcing the use of consistent code style conventions and file organisation which in turn enables automated generation of simple documentation at every CHEM module update. <!-- All model data-structures and algorithms are therefore always documented (at least minimally, with machine authored content), meaning model developers have a requirement to write customised documentation less frequently. Many of the  -->

<!-- It is also important to highlight that  -->
Our framework addresses barriers to <!-- health economic model  -->transferability specific to how a model is implemented as software (ie, CHEMs). Health economists must also consider conceptual or theoretical validity<!-- issues -->. For example, the candidate models currently available in our scorz library [@hamilton_matthew_2022_6084824] were chosen because of their suitability for mapping to the utility instrument (AQoL-6D [@Richardson2012AQ]) used in the study [@Hamilton2021.07.07.21260129] for which scorz was originally developed. We have identified a need to use alternative models for mapping to utility instruments that produce less continuous total score distributions [@Hamilton2021.07.07.21260129]. Our software framework is designed to make such extensions more straightforward to implement.

Factors such as <!-- user enjoyment,  -->usability, active user-community and supporting resources influence adoption of software frameworks [@myllarniemi2018development]. To systematically address these issues for our prototype software framework would require investments in engaging the health economic modelling community to refine framework user requirements, software re-development and testing to meet those requirements, integration with evolving code and documentation authoring capabilities of large language models, the development of improved and more comprehensive documentation and training resources and proactive user-community building and support. We currently lack the resources to undertake these tasks.

Adequately planned, resourced and implemented software frameworks are potentially important enablers of improved health economic modelling practice. Reference models [@Afzali2013], methodological innovation to improve model transferability [@craig2018taking] and the development of regularly updated CHEMs that can support "living Health Technology Assessment" [@thokala2023living] would all be facilitated by a trusted software framework for implementing more transparent, reusable and updatable CHEMs. <!-- However, better tools alone are insufficient and policy and institutional changes are also required.  --><!-- Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful. Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work and funding is rarely adequate to maintain and routinely update a model. Currently, it can take “an extraordinary amount of idealism” to commit to authoring and maintaining research software [@anzt2020environment]. Previously recommended strategies for more beneficial health economic research investments include support for harmonised ethical standards for model development [@10.3389/fpubh.2017.00068], methodological innovation to improve model transferability [@craig2018taking], networks of modellers working on common health conditions [@Sampson2019], and  centralized infrastructure such as open source model repositories [@Pouwels2022] and a standard platform for model implementations [@Ghabri2019]. Development of software frameworks to support ethical CHEM implementations could enable and enhance each of these strategies. --> A future software framework for CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health and health economics, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions. Such approaches will likely be important to ensure a sufficient potential user-base to make CHEM software frameworks sustainable.

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
ready for comparison

MUR 6) *Utility prediction tools* that: (i) search open access repositories for utility mapping models developed with readyforwhastnext; (ii) retrieve relevant metadata, including a link to the model catalogue for models specified by a user; (iii) apply selected utility mapping models to make out of sample predictions using a dataset provided by a user; and (iv) (where there is health utility data at two time points) convert predicted health utility scores to Quality Adjusted Life Years (QALYs).

@@

### Reporting templates
We used the framework reporting tools library to author two reporting templates that are designed to be used in conjunction with these utility mapping modules. The first reporting template [@hamilton_matthew_2022_6116385] is used to create a catalogue of utility mapping models. The second reporting template [@matthew_p_hamilton_2022_5976988] can be used to generate a manuscript providing a scientific summary of each study implemented with these modules.

@@

## Documentation website
Using the framework website as a template, we used the search and documentation tools from our foundation framework library to create and help maintain a project documentation website (https://readyforwhatsnext.org/). The project website includes details on available model modules, datasets and analysis programs and tutorials on how these artefacts can be used.

## Transferability assessment
We subjectively assessed these utility mapping model artefacts against <!-- Edit_start -->TRU criteria <!-- Edit_end --> (Table \@ref(tab:checktb)). For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”. We believe that our utility mapping study module libraries, code and data repositories and documentation have satisfactorily met four of the six criteria (T1, R1, R2 and U1) and have partially met two criteria (T2 and U2). The main shortcomings that we identified when applying the assessment criteria was that individual modules and functions have yet to: (i) be supported with human authored documentation that includes examples of how they can be used; and (ii) be quality assured through unit testing.

>>>>

MUR 6) *Utility prediction tools* that: (i) search open access repositories for utility mapping models developed with readyforwhatsnext; (ii) retrieve relevant metadata, including a link to the model catalogue for models specified by a user; (iii) apply selected utility mapping models to make out of sample predictions using a dataset provided by a user; and (iv) (where there is health utility data at two time points) convert predicted health utility scores to Quality Adjusted Life Years (QALYs).

@@

### Reporting templates
We used the ready4show library to author two reporting templates that are designed to be used in conjunction with these utility mapping modules. The first reporting template [@hamilton_matthew_2022_6116385] is used to create a catalogue of utility mapping models. The second reporting template [@matthew_p_hamilton_2022_5976988] can be used to generate a manuscript providing a scientific summary of each study implemented with these modules.

@@

## Documentation website
Using the framework website as a template, we used the search and documentation tools from the ready4 library to create and maintain a project documentation website (https://readyforwhatsnext.org/). The project website includes details on available model modules, datasets and analysis programs and tutorials on how these artefacts can be used.

## Transferability assessment
We subjectively assessed these utility mapping model artefacts against <!-- Edit_start -->TRU criteria<!-- Edit_end --> (Table \@ref(tab:checktb)). For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”. We believe that our utility mapping study module libraries, code and data repositories and documentation have satisfactorily met four of the six criteria (T1, R1, R2 and U1) and have partially met two criteria (T2 and U2). The main shortcomings we identified were that individual modules and functions have yet to: (i) be supported with human authored documentation that includes examples of how they can be used; and (ii) be quality assured through unit testing.

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
ready for comparison

Potential future directions for readyforwhatsnext may incorporate projects in two additional domains: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce). Our ultimate aim is for readyforwhatsnext to flexibly combine its constituent parts in analyses that help answer questions in a further two domains:

@@

## Transferability
We are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia. Australian public mental health services can be planned and commissioned by the Australian Government, the governments of Australia's state and territories and independent organisations focused on smaller regions called Primary Health Networks. Promoting mentally healthy local communities is also an important role for Australian local governments. The mental health of young people is a global priority [@https://doi.org/10.1002/wps.20938] and Australia has initiated youth mental health service model reforms that have been adopted in other jurisdictions [@RN27]. For these reasons, we aim to develop readyforwhatsnext in a manner that facilitates its transfer to multiple decision contexts.

However, there are ethical risks associated with each potential transfer, in particular the need to ensure the social acceptability, fitness for purpose and appropriate use of a CHEM in each new decision context [@ethicsCHEMS2024]. For that reason, we have set the goal of readyforwhatsnext meeting six explicit criteria for transparency, reusability and updatability (TRU criteria). We have described these criteria and their origins in ethical modelling practice elsewhere [@ethicsCHEMS2024], but briefly they are:

@@

To achieve these goals we are implementing readyforwhatsnext as an open-source, modular model. Open source projects grant third parties liberal permissions to access, use and modify model source code and data. A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular]. <!-- Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering]. -->We are developing readyforwhatsnext using real Australian data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making). To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are also creating toy datasets. Toy data created for illustration purposes is prominently labelled as not for use in decision-analysis.
<!-- PHNS -->
A high level schematic guiding our implementation of readyforwhatsnext as a transferable CHEM is outlined in Figure \@ref(fig:fig1).

>>>>

Potential future directions for readyforwhatsnext may incorporate projects in two additional domains: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce). Our ultimate aim is to flexibly combine model components in analyses that answer questions in a further two domains:

@@

## Transferability
We are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia. Australian public mental health services can be planned and commissioned by the Australian Government, the governments of Australia's state and territories and independent organisations focused on smaller regions called Primary Health Networks. <!-- Promoting mentally healthy local communities is also an important role for Australian local governments. -->The mental health of young people is a global priority [@https://doi.org/10.1002/wps.20938] and Australia has initiated youth mental health service model reforms that have been adopted in other jurisdictions [@RN27]. For these reasons, we aim to develop readyforwhatsnext in a manner that facilitates its transfer to multiple decision contexts.

However, there are ethical risks associated with each potential transfer, in particular the need to ensure the social acceptability, fitness for purpose and appropriate use of a CHEM in each new decision context [@ethicsCHEMS2024]. We therefore aim for readyforwhatsnext to meet six *transparency*, *reusability* and *updatability* (TRU) criteria. We have described these criteria and their origins in ethical modelling practice elsewhere  [@ethicsCHEMS2024], but briefly they are:

@@

To meet these criteria we are implementing readyforwhatsnext as an open-source, modular model. Open source projects grant third parties permissions to access, use and modify model source code and data. A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular]. <!-- Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering]. -->When undertaking analyses intended to inform decision-making, readyforwhatsnext uses real Australian data (which can be empirical, simulated or assumption-based). To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are creating toy datasets. <!-- PHNS -->A high-level schematic guiding our implementation of readyforwhatsnext is outlined in Figure \@ref(fig:fig1).

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
ready for comparison

To help readyforwhatsnext meet all six TRU criteria, we developed a prototype software framework. The software framework is called ready4 [@ready424].

## Framework user requirements
We created ready4 with one primary user group in mind - ourselves. The framework user requirements (FURs) for ready4 evolved over six years (2018-2024) as we became aware of new issues that we needed to solve. Currently, these requirements are:

FUR 1) A reusable *template* for CHEM modules that can: (i) be run as independent models; (ii) safely combined, sharing inputs and outputs with each other without unintended interference; and (iii) be selectively replaced, updated or extended.

@@

FUR 3) *Module authoring tools* that integrate with online software development services to help author R libraries of CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) always at least minimally documented; (iv) licensed for reuse; (v) bundled with authorship, funding source, version number and Digital Object Identifier (DOI) metadata; and (vi) quality assured with publicly available testing artefacts.

@@

FUR 5) *Reporting tools* that: help (i) author reporting templates for rendering documents in HTML, Adobe PDF and Microsoft Word file formats; (ii) retrieve version specific reporting templates from online code repositories and (iii) supply study specific data (e.g authorship details, input data and analysis results) to reporting templates to render custom reports and scientific summaries.
<!-- help generate tables for multiple outputs, retrieve templates, modify templates with authorship and results -->

FUR 6) *Search tools* to retrieve web based information on a CHEM project's: (i) publicly available model modules, module libraries and tutorials; (ii) datasets and data collections; and (iii) replication programs and reporting templates.

@@

### R libraries 
A library in the R language will typically depend on multiple other R libraries, many of which are likely to have different authors. As the number of third-party dependencies of an R library grows so does the fragility of that library (e.g., the library may cease to work as intended due to changes in one of its dependency libraries). To reduce the fragility of our framework we implemented it as multiple R libraries rather than one R library. In total we authored six novel R libraries to implement the ready4 framework, all of which have distinct purposes and dependencies (Table \@ref(tab:cpkgs)).

One library provides the foundation for the ready4 framework. <!-- In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].  -->To meet *FUR 1*, the ready4 [@ready4lib24] foundation library defines a template CHEM module using R’s S4 class system, that supports an object-oriented programming paradigm. Two notable features of object-oriented programming are encapsulation [@8717448] and inheritance [@8717448]. Encapsulation allows a CHEM module to bundle model data and algorithms in a protected environment, which is useful for helping ensure that CHEM modules continue to work as intended when combined<!-- [@ready4oop2022] -->. Inheritance allows new CHEM modules to inherit some or all of the properties of a parent module. Inheritance is useful when it is necessary to selectively modify CHEM modules, for example to account for: (i) interaction effects when CHEMs are combined; or (ii) distinctive features of a new decision contexts to which they are being transferred<!-- [@ready4oop2022] -->. The ready4 template CHEM module can be used to create other CHEM modules that inherit a common set of properties. One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named (meeting *FUR 2*). The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with ready4 (meeting *FUR 6*) and tools for developing and maintaining a CHEM project's documentation website (meeting *FUR 7*).

Three framework module authoring libraries are designed to meet *FUR 3*. <!-- Define functional and object-oriented approaches, acceptance and unit testing. -->The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452]. Authoring with each of these paradigms is supported by ready4. The ready4fun [@ready4funlib24] library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function. The ready4class [@ready4classlib24] library contains tools to help streamline and standardise the authoring of novel, documented CHEM modules from the template CHEM module. The ready4pack [@ready4packlib24] library provides tools for disseminating themed bundles of CHEM modules as R libraries that are: documented (with a website and PDF manuals); licensed (using the copyleft GNU GPL-3 [66] by default); easily citable (citation information can be retrieved within an R session or from hosting repositories); and quality assured (each update triggers the running of any tests created by module library authors, with test results publicly documented).

@@

###	Online services 
Framework libraries are designed to be used in conjunction with a number of third-party online services. The framework's module authoring tools use the GitHub [@github2007] service's tools for: software development, testing, version control and distribution; hosting of documentation websites; and transparent record keeping of collaborator contributions. The continuous integration [@CI2017] tools provided by GitHub are used to trigger systematic retesting of module libraries with every edit. <!-- Imported -->These tests can be unit tests (to verify that small, isolated sections of code produce the correct output when run independently) and acceptance tests (to verify that the correct output is produced when multiple code components are run together to perform tasks that meet core user-requirements [@martin2003agile]). A useful concept for informing software users about the extensiveness of testing procedures is code coverage [@ERICWONG2010188] - reports of the proportion of code that has been explicitly tested. The module authoring libraries use the codecov [@codecov_2022] service to measure and share information about code coverage. <!-- End_Imported -->The open science repository service Zenodo [@Zenodo2013] is used by the module authoring libraries to provide persistent storage, uniquely identified with a Digital Object Identifier (DOI), of each code release. The framework's data management tools use the Dataverse [@Dataverse2007] data repository service for persistent, uniquely identifiable and versioned storage of model input and output data. For the management of frequently updated datasets that do not require persistent storage, all framework libraries use GitHub.

###	Documentation website
A project documentation website (https://www.ready4-dev.com) provides guidance to model developers on how to use and contribute improvements to the ready4 software framework. The documentation website is versioned, which means documentation relating to prior versions of framework software can be archived, retrieved and viewed. The documentation website was developed using the Hugo framework [@hugo_2023], Docsy theme [@docsy_2023] and Algolia DocSearch [@algoliadocsearch_2023] and is hosted using the Netlify [@netlify_2023] service. We linked our Netlify account to our GitHub organisation so that the project website would automatically update whenever its source code (publicly available in a GitHub repository) was edited.

>>>>

To help readyforwhatsnext meet all six TRU criteria, we developed a prototype software framework called ready4 [@ready424].

## Framework user requirements
<!-- We created ready4 with one primary user group in mind - ourselves.  -->The framework user requirements (FURs) for ready4 evolved over six years (2018-2024) as we encountered new implementation issues for readyforwhatsnext that we needed to solve. Currently, these requirements are:

FUR 1) A reusable *template* for CHEM modules that can be: (i) run as independent models; (ii) safely combined, sharing inputs and outputs with each other without unintended interference; and (iii) selectively replaced, updated or extended.

@@

FUR 3) *Module authoring tools* that integrate with online software development services to help author CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) always at least minimally documented; (iv) licensed for reuse; (v) bundled as R libraries with authorship, funding source, version number and Digital Object Identifier (DOI) metadata; and (vi) quality assured with publicly available testing artefacts.

@@

FUR 5) *Reporting tools* that: help (i) author reporting template programs for rendering HTML, Adobe PDF and Microsoft Word outputs; (ii) retrieve version specific reporting template programs from online code repositories and (iii) supply reporting template programs with study specific data (e.g., authorship details, input data and analysis results) to render custom reports.
<!-- help generate tables for multiple outputs, retrieve templates, modify templates with authorship and results -->

FUR 6) *Search tools* to retrieve web-based information on a CHEM project's: (i) model modules and tutorials; (ii) datasets and data collections; and (iii) replication and reporting template programs.

@@

### R libraries 
R libraries typically depend on multiple other R libraries<!-- , many likely to have different authors -->. As the number of dependencies of an R library grows, so does the fragility of that library (e.g., the library may cease to work as intended due to changes in one of its dependency libraries). To reduce the fragility of our framework we implemented it as multiple R libraries rather than one R library. We authored six novel R libraries to implement the ready4 framework, all of which have distinct purposes and dependencies (Table \@ref(tab:cpkgs)).

<!-- In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].  -->To meet *FUR 1*, the ready4 [@ready4lib24] foundation library defines a template CHEM module using R’s S4 class system, that supports an object-oriented programming paradigm. Two notable features of object-oriented programming are encapsulation [@8717448] and inheritance [@8717448]. Encapsulation allows a CHEM module to bundle model data and algorithms in a protected environment, which is useful for helping ensure that CHEM modules continue to work as intended when combined<!-- [@ready4oop2022] -->. Inheritance allows new CHEM modules to inherit some or all of the properties of a parent module. Inheritance is useful when modifying CHEM modules, for example to account for: (i) interaction effects when CHEMs are combined; or (ii) distinctive features of a new decision contexts to which they are being transferred<!-- [@ready4oop2022] -->. The ready4 template CHEM module can be used to create other CHEM modules that inherit a common set of properties. One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named and described (meeting *FUR 2*). The ready4 library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs (meeting *FUR 6*) and tools for developing and maintaining a CHEM project's documentation website (meeting *FUR 7*).

Three module authoring libraries are designed to meet *FUR 3*. <!-- Define functional and object-oriented approaches, acceptance and unit testing. The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452]. Authoring with each of these paradigms is supported by ready4. -->The ready4fun [@ready4funlib24] library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function. The ready4class [@ready4classlib24] library contains tools to help streamline and standardise the authoring of novel, documented CHEM modules from the template CHEM module. The ready4pack [@ready4packlib24] library provides tools for disseminating themed bundles of CHEM modules as R libraries that are: documented (with a website and PDF manuals); licensed (using the copyleft GNU GPL-3 [66] by default); easily citable (citation information can be retrieved within an R session or from hosting repositories); and quality assured (each update triggers the running of any tests created by module library authors, with test results publicly documented).

@@

###	Online services 
Framework libraries are designed to be used in conjunction with a number of online services. The  module authoring libraries use the GitHub [@github2007] service's tools for: software development, testing, version control and distribution; hosting of documentation websites; and transparent record keeping of collaborator contributions. Continuous integration [@CI2017] tools provided by GitHub are used to trigger systematic retesting of module libraries with every edit. <!-- Imported -->Tests can be unit tests (verifying the correct output when small, isolated sections of code are run independently) and acceptance tests (verifying the correct output from multiple code components are run together to meet core user-requirements [@martin2003agile]). <!-- A useful concept for informing software users about the extensiveness of testing procedures is .  -->The module authoring libraries use the codecov [@codecov_2022] service to measure and share information about code coverage [@ERICWONG2010188] - the proportion of code that has been explicitly tested. <!-- End_Imported -->The open science repository service Zenodo [@Zenodo2013] is used by the module authoring libraries to provide persistent storage, uniquely identified with a Digital Object Identifier (DOI), of each code release. The ready4use library uses the Dataverse [@Dataverse2007] data repository service for persistent, uniquely identifiable and versioned storage of model input and output data. For the management of frequently updated datasets that do not require persistent storage, all framework libraries use GitHub.

###	Documentation website
A project documentation website (https://www.ready4-dev.com) provides guidance to model developers on how to use and contribute improvements to the ready4 software framework. Prior versions of the documentation website are archived and publicly accessible. The documentation website was developed using the Hugo framework [@hugo_2023], Docsy theme [@docsy_2023] and Algolia DocSearch [@algoliadocsearch_2023] and is hosted using the Netlify [@netlify_2023] service. We linked our Netlify account to our GitHub organisation so that the project website automatically updates whenever its (publicly available) source code is edited.

### 2024-03-01 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
ready for comparison

<!-- Imported_from_Ethics-->Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39]. Health economic models are likely to require at least some modification before they can be validly applied to a new jurisdiction, time period or decision problem. The difficulty of undertaking such a model transfer depends in part on whether third parties can readily understand, use and edit the software files that implement the model - the Computational Health Economic Model (CHEM).

@@

Some of the barriers<!-- Give examples --> to the development of transferable CHEMs <!-- that use open-source and modular approaches  -->could be addressed by appropriate software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development]. A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs. Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers [@edwin2014software]. Software frameworks have widely been developed and implemented in data science, for example, PyTorch [@PyTorch2019] for machine learning using Python. However, software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software]. Software frameworks can also be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].

>>>>

<!-- Imported_from_Ethics-->Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (application of selected components and/or application with modification) [@RN39]. Health economic models are likely to require at least some modification before they can be validly applied to a new jurisdiction, time period or decision problem. Making such modifications is harder if the software files that implement the model - the Computational Health Economic Model (CHEM) – cannot be readily understand, used and edited.

@@

Some of the barriers<!-- Give examples --> to the development of transferable CHEMs <!-- that use open-source and modular approaches  -->could be addressed by appropriate software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software <!-- and which is not typically visible to software end-users  -->[@myllarniemi2018development]. A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs. Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers [@edwin2014software]. <!-- Software frameworks have widely been developed and implemented in data science, for example, PyTorch [@PyTorch2019] for machine learning using Python. However, software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software]. Software frameworks can also be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development]. -->
